A large-scale analysis of racial disparities in police stops across the United

### 2019-12-10 lib/paper_results.Rmd
update for paper

```{r disparity-state-hit_rates-plot, fig.height=6, fig.width=10}
disp$state$outcome$plots$aggregate + theme(legend.position = "none")
```

@@

```{r disparity-thresholds-tables}
kable(disp$city$threshold$results$aggregate_thresholds)
kable(disp$state$threshold$results$aggregate_thresholds)
```

@@

```{r disparity-city-thresholds-plot, fig.height=5, fig.width=10}
axis_min <- max(
  min(
    disp$city$threshold$plots$aggregate$data$minority_rate,
    disp$city$threshold$plots$aggregate$data$majority_rate
  ) - 0.05, 0
)
axis_max <- min(
  max(
    disp$city$threshold$plots$aggregate$data$minority_rate,
    disp$city$threshold$plots$aggregate$data$majority_rate
  ) + 0.05, 1
)
disp$city$threshold$plots$aggregate + 
  theme(legend.position = "none", plot.title = element_blank()) + 
  scale_x_continuous(
    limits = c(axis_min, axis_max), breaks = seq(0, .5, 0.05),
    labels = scales::percent_format(accuracy = 1), expand = c(0,0)
  ) + 
  scale_y_continuous(
    limits = c(axis_min, axis_max), breaks = seq(0, .5, 0.05),
    labels = scales::percent_format(accuracy = 1),expand = c(0,0)
  ) 
```

@@

```{r disparity-state-thresholds-plot, fig.height=5, fig.width=10}
disp$state$threshold$plots$aggregate + theme(legend.position = "none")
```

@@

```{r disparity-city-ppc-search, fig.height=5, fig.width=8}
disp$city$threshold$ppc$search_rate
```

@@

```{r disparity-city-ppc-hit, fig.height=5, fig.width=8}
disp$city$threshold$ppc$hit_rate
```

@@

```{r disparity-state-ppc-search, fig.height=5, fig.width=8}
disp$state$threshold$ppc$search_rate
```

@@

```{r disparity-state-ppc-hit, fig.height=5, fig.width=8}
disp$state$threshold$ppc$hit_rate
```

>>>>

```{r disparity-state-hit_rates-plot, fig.height=6, fig.width=10}
axis_min <- max(
  min(
    disp$state$outcome$plots$aggregate$data$minority_rate,
    disp$state$outcome$plots$aggregate$data$majority_rate
  ) - 0.05, 0
)
axis_max <- min(
  max(
    disp$state$outcome$plots$aggregate$data$minority_rate,
    disp$state$outcome$plots$aggregate$data$majority_rate
  ), 1
)
disp$state$outcome$plots$aggregate + 
  theme(
    legend.position = "none",
    plot.title = element_blank()
  ) +
  scale_x_continuous(
    limits = c(axis_min, axis_max),
    labels = scales::percent_format(accuracy = 1), expand = c(0,0)
  ) + 
  scale_y_continuous(
    limits = c(axis_min, axis_max),
    labels = scales::percent_format(accuracy = 1),expand = c(0,0)
  ) 
```

@@

```{r disparity-thresholds-tables}
kable(disp$city$threshold$prior_scaling_factor_1$results$aggregate_thresholds)
kable(disp$state$threshold$prior_scaling_factor_1$results$aggregate_thresholds)
```

@@

```{r disparity-city-thresholds-plot, fig.height=5, fig.width=10}
axis_min <- max(
  min(
    disp$city$threshold$prior_scaling_factor_1$plots$aggregate$data$minority_rate,
    disp$city$threshold$prior_scaling_factor_1$plots$aggregate$data$majority_rate
  ) - 0.05, 0
)
axis_max <- min(
  max(
    disp$city$threshold$prior_scaling_factor_1$plots$aggregate$data$minority_rate,
    disp$city$threshold$prior_scaling_factor_1$plots$aggregate$data$majority_rate
  ) + 0.05, 1
)
disp$city$threshold$prior_scaling_factor_1$plots$aggregate + 
  theme(legend.position = "none", plot.title = element_blank()) + 
  scale_x_continuous(
    limits = c(axis_min, axis_max), breaks = seq(0, .5, 0.05),
    labels = scales::percent_format(accuracy = 1), expand = c(0,0)
  ) + 
  scale_y_continuous(
    limits = c(axis_min, axis_max), breaks = seq(0, .5, 0.05),
    labels = scales::percent_format(accuracy = 1),expand = c(0,0)
  ) 
```

@@

```{r disparity-state-thresholds-plot, fig.height=5, fig.width=10}
disp$state$threshold$prior_scaling_factor_1$plots$aggregate + 
  theme(
    legend.position = "none",
    plot.title = element_blank()
  )
```

@@

```{r disparity-city-ppc-search, fig.height=5, fig.width=8}
disp$city$threshold$prior_scaling_factor_1$ppc$search_rate
```

@@

```{r disparity-city-ppc-hit, fig.height=5, fig.width=8}
disp$city$threshold$prior_scaling_factor_1$ppc$hit_rate
```

@@

```{r disparity-state-ppc-search, fig.height=5, fig.width=8}
disp$state$threshold$prior_scaling_factor_1$ppc$search_rate
```

@@

```{r disparity-state-ppc-hit, fig.height=5, fig.width=8}
disp$state$threshold$prior_scaling_factor_1$ppc$hit_rate
```
